Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-08-08 article.rnw
Add the acknowledgements.
Change weighted_coclassification_kable and grouped_alpha_matrix to return strings.
They previously directly printed their output, which prohibited saving it usefully.

	\begin{subfigure}{\textwidth}
		\centering
		<<>>=
			grouped_alpha_matrix(
				best_species_names,
				best_row_grouping,
				best_col_grouping,
				best_alpha_matrix
			)
		@
		\caption{Grouped alpha matrix}
		\label{fig:best-alpha-matrix}
	\end{subfigure}

@@

	\begin{subfigure}{0.49\textwidth}
		\centering
		<<>>=
			minimal_coclassification_kable(
				best_col_coclassification,
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			)
		@
		\caption{Coclassification of competitive effects\\(columns)}
		\label{fig:best-coclassification-cols}
	\end{subfigure}
	%
	\begin{subfigure}{0.49\textwidth}
		\centering
		<<>>=
			minimal_coclassification_kable(
				best_row_coclassification,
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			)
		@
		\caption{Coclassification of competitive responses\\(rows)}
		\label{fig:best-coclassification-rows}
	\end{subfigure}

@@

\begin{figure}
	\centering
	\begin{subfigure}{\textwidth}
		\centering
		<<>>=
			weighted_coclassification_kable(
				weighted_col_coclassification_matrix[species_output_order,species_output_order],
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			)
		@
		\caption{Coclassification of competitive effects}
		\label{fig:coclassification-cols}
	\end{subfigure}

@@

	\begin{subfigure}{\textwidth}
		\centering
		<<>>=
			weighted_coclassification_kable(
				weighted_row_coclassification_matrix[species_output_order,species_output_order],
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			)
		@
		\caption{Coclassification of competitive responses}
		\label{fig:coclassification-rows}
	\end{subfigure}

@@

>>>>

	\begin{subfigure}{\textwidth}
		\centering
		<<>>=
			cat(grouped_alpha_matrix(
				best_species_names,
				best_row_grouping,
				best_col_grouping,
				best_alpha_matrix
			))
		@
		\caption{Grouped alpha matrix}
		\label{fig:best-alpha-matrix}
	\end{subfigure}

@@

	\begin{subfigure}{0.49\textwidth}
		\centering
		<<>>=
			cat(minimal_coclassification_kable(
				best_col_coclassification,
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			))
		@
		\caption{Coclassification of competitive effects\\(columns)}
		\label{fig:best-coclassification-cols}
	\end{subfigure}
	%
	\begin{subfigure}{0.49\textwidth}
		\centering
		<<>>=
			cat(minimal_coclassification_kable(
				best_row_coclassification,
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			))
		@
		\caption{Coclassification of competitive responses\\(rows)}
		\label{fig:best-coclassification-rows}
	\end{subfigure}

@@

\begin{figure}
	\centering
	\begin{subfigure}{\textwidth}
		\centering
		<<>>=
			cat(weighted_coclassification_kable(
				weighted_col_coclassification_matrix[species_output_order,species_output_order],
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			))
		@
		\caption{Coclassification of competitive effects}
		\label{fig:coclassification-cols}
	\end{subfigure}

@@

	\begin{subfigure}{\textwidth}
		\centering
		<<>>=
			cat(weighted_coclassification_kable(
				weighted_row_coclassification_matrix[species_output_order,species_output_order],
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			))
		@
		\caption{Coclassification of competitive responses}
		\label{fig:coclassification-rows}
	\end{subfigure}

@@

\section{Acknowledgements}

I would like to thank Hao Ran Lai for feedback on a draft of the manuscript.

DBS is also grateful for the support of the Marsden Fund Council, from New Zealand Government funding (grant 16-UOC-008).
